% -*- Mode: LaTeX -*-
%        File: legal.tex
%      Author: Bryan Jurish <moocow@ling.uni-potsdam.de>
% Description: know rules: admin: legal stuff
%
%---------------------------------------------------------------------------
% \subsection{Legal Stuff}\label{legal}
%---------------------------------------------------------------------------

This document, the \latex{\knowlatex}\html{\knowhtml}\ logo,
and the \know\ board as printed
herein are Copyright \copyright\ 2001 by Bryan Jurish,  all rights reserved.
The original {\sl know} rulebook, circular and square boards are
Copyright \copyright\ 1995, 2001 by Bryan Jurish, all rights reserved.

\know\ is a free game.  You may copy, modify, and/or redistribute
this document in whole or in part, in any medium physical or electronic,
as long as this copyright notice is retained on all copies.

\subsubsection{Commercial Distribution}\label{commercial}

Commercial distribution of \know\ and derivative works is allowed
according to the conditions outlined below.
For purposes of these conditions, the GAME refers to this document
and/or works derived from it, as well as \know\ game boards and/or their
derivatives.  The DISTRIBUTOR refers to any individual, collective, corporation,
or other entity distributing the GAME for commercial purposes,
including trade and barter.  The SELLER refers to any DISTRIBUTOR
distributing the GAME for monetary reimbursement.
The AUTHOR refers to the author of this document, Bryan Jurish.

\begin{enumerate}
  \item
    The DISTRIBUTOR must make this document available in some
    form to the general public free of charge,
    for instance by making an electronic copy accessible for
    download via an http server on the internet.

    If the DISTRIBUTOR does not have access to such an
    electronic distribution medium, then this condition may be
    met by allowing public viewing of a printed version of this
    document at all sites of end-user distribution (sales outlets).

  \item
    The SELLER must contact the AUTHOR and notify the
    AUTHOR of the SELLER's intent to produce a distribution
    for monetary reimbursement.  See \secref{feedback} for information
    on how to contact the AUTHOR.
\end{enumerate}

%
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "~/text/projects/know/tex/know"
%%% End: 
